\documentclass[margin,line]{resume}
\usepackage[defblank]{paralist}
\usepackage{pdfpages}
\usepackage{anysize}
\usepackage{fancyhdr}
\usepackage{datetime}
\usepackage[pdftex, unicode]{hyperref}
\hypersetup{
	pdftitle={Zachary Hart's Resume},
	pdfauthor={Zachary Hart},
	pdfborder={0 0 0},
	% Not sure if this is needed.
	unicode=true
}

\marginsize{0.75in}{2.0in}{0.75in}{0.5in}
\setdefaultitem{\footnotesize \textbullet}{}{}{}{}{}
\setdefaultleftmargin{0em}{}{}{}{}{}
\setdefaultenum{(a)}{(1)}{}{}{}{}
\newcommand{\rurl}[1]{\hfill {\footnotesize \url{#1}}}
\newcommand{\rdate}[1]{\hfill {\small #1}}
\renewcommand{\employer}[5]{\item[#1] - #2 \rdate{#3} \\* #4 \rurl{#5} \\*}
\renewcommand{\headrulewidth}{0.0pt} % remove HR added by \pagestyle{fancy}
\fancyhf{}
\fancyfoot[R]{\footnotesize Updated: \today}
\pagestyle{fancy}
\begin{document}
\name{\Huge Zachary Hart}

\begin{resume}
\section{\mysidestyle Contact Information}
	\begin{asparablank}
		\item \href{mailto:zach@zthart.me}{zach@zthart.me} \rurl{https://github.com/zthart}
		\item (972) 786-5794 \rurl{https://linkedin.com/in/zthart}
    	\end{asparablank}

\section{\mysidestyle Objective}
	\begin{asparablank}
	\item To improve the material conditions for all through accessible, innovative technology.
        \normalsize
	\end{asparablank}

\section{\mysidestyle Education}
	\begin{asparablank}
	\item{\bf Rochester Institute of Technology} - Rochester, NY \rurl{https://rit.edu}
		\small \item B.S. Computer Science \rdate{August 2015 - December 2019}
	\end{asparablank}

\section{\mysidestyle Work Experience}
	\begin{asparablank}

    \item{\bf Okta} - San Francisco, CA \rurl{https://okta.com}
    \small \item Sr. Software Engineer - Identity Ecosystem \hfill Aug 2021 - Present \\

    \small A member of the \textbf{atSpoke} team within Okta's Identity Ecosystem engineering org.
    \small \textbf{Full-stack} engineer working to bring a robust web-based workflow system to Okta's upcoming IGA offering.
    \small Participated in integration efforts between the atSpoke team and the existing Identity Ecosystem org, as well as growing the team through hiring and onboarding of new engineers.
    \normalsize
    \\
    \item{\bf atSpoke} - San Francisco, CA \rurl{https://atspoke.com}
    \small \item Software Engineer II \hfill February 2021 - August 2021
    \small \item Software Engineer I \hfill January 2020 - Februrary 2021 \\

    \small \textbf{Full-stack} engineer developing a \textbf{React} web application with a \textbf{Node.js} backend.
    \small Worked directly on a cross-functional team to complete a migration and redesign of the application's frontend framework from \textbf{Angular} to React.
    \small Lead technical design efforts on a number of key product features and improvements, including atSpoke's \textbf{Workflows} system.
    \small Developed and tested new features efficiently as a member of a globally distributed team, as well as a sole engineer, until the company's acquisition by \textbf{Okta} in August 2021.
    \normalsize
    \\
	\item{\bf Blackbaud} - Charleston, SC \rurl{https://blackbaud.com}
	\small \item Software Engineer Intern - Full Stack \hfill May 2019 - August 2019 \\

	\small A member of the \textbf{Data Intelligence} group, developing applications to better facilitate customer interaction with their data.
	\small Utilizing \textbf{Angular} and \textbf{.NET Core}, backed by \textbf{Azure} cloud services, migrated existing services to a microservice architecture.
	\small Developed and tested microservices in an environment with a robust Azure DevOps \textbf{CI}/\textbf{CD} release pipeline.
	\small Created platform services for the management and export of user-created lists of metadata-driven data.
	\normalsize
	\end{asparablank}

\section{\mysidestyle Technical Skills}
	\begin{compactdesc}
		\item[Languages] \begin{inparaenum} { \small
			Python, C\#, Java, C, Javascript, Typescript
		} \end{inparaenum}
        \item[Frameworks, Libraries, \& Tools] \begin{inparaenum} { \small
			Flask, Django, Requests, Pytest, SQL, MongoDB, .NET Core, Angular, React, Jest, Mocha, GCP/AWS/Azure Cloud Services (Azure DevOps)
        } \end{inparaenum}
		\item[Operating Systems] \begin{inparaenum} { \small
			Linux (CentOS/RHEL/Fedora, Debian/Ubuntu), Windows, macOS
		} \end{inparaenum}
        \normalsize
	\end{compactdesc}

\section{\mysidestyle Projects}
	\begin{asparablank}
        \item {\bf Mizu \& Potion Seller } \rurl{https://github.com/zthart/mizu}

        \small A duo of \textbf{RESTful API}s for the web-connected vending machines at RIT's 
        \textit{Computer Science House}. Written in \textbf{Python}, leveraging the \textbf{Flask} microframework, 
        the API enables any member to drop drinks having authenticated with internal SSO. Designed and built 
        alongside a rewrite of the web application.
        \\
		\item {\bf Pourover}\rurl{https://github.com/zthart/pourover}

		\small A \textbf{Python} library for parsing and manipulating CEF messages and log files - used in production in 
        an enterprise environment, and available on pypi.
		\normalsize
		\\
		\item {\bf Huffman Lite}

		\small Written in \textbf{C}, Huffman Lite is a huffman-like encoding and compression algorithm. Utilizing a 
        tree structure similar to a huffman tree, Huffman Lite can encode and decode both human readable files and 
        binary files.
		\normalsize
	\end{asparablank}

% \section{\mysidestyle Extracurricular}
% 	\begin{asparablank}
% 		\item {\bf CSH ({\small Computer Science House})}\rurl{http://www.csh.rit.edu/}
% 		\small	\item House Improvements Director \hfill August 2016 - June 2017
%         \small  \item Drink Administrator \hfill March 2016 - December 2019
%         \linebreak
% 
%         \small Computer Science House, or CSH, is a group of technically-minded students at the Rochester Institute of Technology that all share a goal of learning and creating through collaboration.
%         \small Members past and present have been responsible for creating many projects that have seen success at RIT, as well as in the public space.
% 	\end{asparablank}


\end{resume}
\end{document}
